### 2018-05-18 manuscript.rmd
new knit with supp. info pdf output fix

All scripts for the analyses are available in a git repository at [https://github.com/caseywdunn/siphonophore_phylogeny_2017](https://github.com/caseywdunn/siphonophore_phylogeny_2017). The most recent commit at the time of the analysis presented here was `r system("git log | head -n 1", intern=TRUE) %>% str_replace("commit ", "")` with tag "paper_v2".

@@

RAxML ML analyses were conducted on the unpartitioned supermatrix using the WAG+$\Gamma$ model of amino acid substitution (Fig. \@ref(phylogeny)A). RAxML bootstrap values were estimated using `r length(bootstrap_trees)` replicates. IQTree ML analyses were run under JTT + Empirically counted frequencies from alignment + FreeRate model with 7 categories, the best model identified by ModelFinder, and the commonly used model GTR + Optimized base frequencies + Free rate model with 6 categories ((Fig. \@ref(fig:supplementary-trees))).

@@

Morphological character data used in trait mapping were obtained from the literature or direct observation of available voucher material. Depth distribution data was queried from the MBARI VARS database ( http://www.mbari.org/products/research-software/video-annotation-and-reference-system-vars/) [@schlining2006mbari]. We used stochastic character mapping to infer the most probable evolution of traits on the tree in R using the `phytools` package [@MEE3:MEE3169; @huelsenbeck2003stochastic]. Subsequent analyses were conducted in R and integrated into this manuscript with the `knitr` package. See Supplementary Information for R package version numbers.

@@

Ancestral character state reconstructions favor the hypothesis that monoecy arose twice (Fig. \@ref(reconstruct)A, \@ref(fig:BI-mono)), once in Calycophorae and once in Clade A. This is consistent with differences in the arrangements of male and female gonophores in the two clades. In Clade A, male and female zooids are found within the same cormidium (a single reiterated sequence of zooids along the stem, see Fig. \@ref(colony)). In these species, the male and female zooids are placed at different but well defined locations within the cormidium. Meanwhile in calycophorans, each cormidium bears either male or female gonophores. In this form of monoecy, the male and female cormidia can either occur in an alternating pattern, or there can be several male or female cormidia in a row. In either case, male and female zooids are found at the same corresponding locations within the cormidia. One known exception to this can be found in abylid calycophorans, where both male or female gonophores may be found within the same eudoxid [@carre1967]. In sum, homoplasy in sexual-system evolution along with variation in the spatial arrangement of gonophores within a colony suggest that siphonophores have evolved different ways to be monoecious. The sexual system and cormidial arrangement of *Rudjakovia* is undescribed, although preliminary observations suggest that this species may be monoecious and that monoecy arose a third time in the Pyrostephidae. A detailed redescription of *Rudjakovia* would help clarify this.

@@

Within Calycophorae there are additional variations of the sexual mode: in *Sulculeolaria* (not included in this phylogeny) colonies appear to consist of only one sex at a time. However they are monoecious and protandrous, with female gonophores developing after the release of male gonophores [@carre1979]. Environmental influences may also play a role in determining the expressed sex. Colonies of the calycophoran *Chelophyes appendiculata* collected in the field always bear both male and female gonophores, whereas when kept in culture only gonophores of one sex are maintained [@Carre:2000hb]. This suggests a high plasticity of the sexual state in some calycophoran taxa and underlines the need for caution when evaluating the state of this character in rarely collected species.

@@

Palpons are typically defined as modified reduced gastrozooids [@mackie1987siphonophore]. In many species palpons are thought to play a role in digestion and circulation of the gastrovascular fluid, while other species may use them for defense (e.g *Physophora*) or sensory functions [@totton1965synopsis]. Palpons are subcategorised based on their location - palpons that are associated with gonodendra are termed gonopalpons (typically with a reduced tentacle, called a palpacle); palpons found along the stem of the siphosome are termed palpons (typically have a tentacle); and palpons found along the stem of the nectosome are termed nectosomal palpons (as in *Apolemia*) [@totton1965synopsis;@siebert2013re]. It is not clear how structure and function differs among different palpon subtypes, and a detailed histological investigation of palpons found at different locations within species is needed. For this reason, here we only assess the presence or absence of palpons as a category, without assessing subtypes of palpons. This presumes that palpons located at different regions in the colony are derived from other palpons rather than each arising *de novo* by independent modification of gastrozooids, a hypothesis that itself could be challenged upon closer histological examination of palpon diversity.

@@

This work was supported by the National Science Foundation (DEB-1256695, the Waterman Award, and DEB-1701272). CM was also supported in part by a RI-EPSCoR Fellowship, NSF EPS-1004057. Sequencing at the Brown Genomics Core facility was supported in part by NIH P30RR031153 and NSF EPSCoR EPS-1004057. Data transfer was supported by NSF RII-C2 EPS-1005789. Analyses were conducted with computational resources and services at the Center for Computation and Visualization at Brown University, supported in part by the NSF EPSCoR EPS-1004057 and the State of Rhode Island. SOWHAT analyses were carried out on the Odyssey cluster supported by the FAS Division of Science, Research Computing Group at Harvard University -- we thank Cassandra Extavour for use of the Harvard cluster. Analyses were also conducted on the Hoffman2 cluster of the Institute for Digital Research and Education of the University of California, Los Angeles. We thank Rob Sherlock for providing the *Bathyphysa conifera* photograph. We also thank Zack Lewis for help with RNA extractions and the MBARI crews and ROV pilots for collection of the specimens.

@@

pdf("supplementary_info/Supplementary_Figure3.pdf")
plot(tentilla_obj)
dev.off()

@@

pdf("supplementary_info/Supplementary_Figure4.pdf")
plot(tentilla2_obj)
dev.off()
```

@@

pdf("supplementary_info/Supplementary_Figure5.pdf")
plot(nectosome_obj)
dev.off()
```

@@

pdf("supplementary_info/Supplementary_Figure6.pdf")
plot(desc_mantle_obj)
dev.off()
```

@@

pdf("supplementary_info/Supplementary_Figure7.pdf")
plot(necto_pos_obj)
dev.off()
```

@@

pdf("supplementary_info/Supplementary_Figure8.pdf")
plot(depthmap)
dev.off()
```

@@

###Bayesian models & model fit {-}

@@

```{r BI tree ancestral trait reconstructions, echo=FALSE, message=FALSE, warning=FALSE, verbose= FALSE,}

@@

#Stochastic trait mapping:
#Make simmap objects
#print("SIMMAP Sex Distribution")
make.simmap(ultratree , sex, nsim = 100, message=FALSE) -> sex_sim
#print("SIMMAP Palpons")
make.simmap(ultratree , palpons, nsim = 100, message=FALSE) -> palpons_sim
#print("SIMMAP Tentilla")
make.simmap(ultratree , tentilla, nsim = 100, message=FALSE) -> tentilla_sim
#print("SIMMAP Tentilla2")
make.simmap(ultratree , tentilla2, nsim = 100, message=FALSE) -> tentilla_sim2
#print("SIMMAP Nectosome")
make.simmap(ultratree , nectosome, nsim = 100, message=FALSE) -> nectosome_sim
#print("SIMMAP Nectosome Position")
make.simmap(ultratree , bracts, nsim = 100, message=FALSE) -> bracts_sim
#print("SIMMAP Habitat")

#Nectophore position SIMMAP setup
NectoPosTree = drop.tip(ultratree , which(!(ultratree $tip.label %in% names(necto_pos))))
make.simmap(NectoPosTree, necto_pos, nsim = 100, message=FALSE) -> necto_pos_sim

#Descending mantle Canal SIMMAP Setup
DescMantleTree =  drop.tip(ultratree , which(!(ultratree $tip.label %in% names(desc_mantle))))
make.simmap(DescMantleTree, desc_mantle, nsim = 100, message=FALSE) -> desc_mantle_sim
```
![\label{bayesian}Bayesian (BI) CAT poisson phylogram with bipartition frequencies from the Bayesian posterior distribution of trees. Unlabeled nodes have support >0.99. The numbers of valid described species estimated to be in each clade based on taxonomy are shown below each clade name on the right.](supplementary_info/Supplementary_Figure11.pdf)

@@

```{r BI-mono, echo=FALSE, message=FALSE, warning=FALSE, verbose= FALSE, fig.width=6.5, fig.height=7, fig.cap= "Brownian Motion character map of sexual characters on the consensus Bayesian tree topology." }
#Simmap SEX
sex_obj <- densityMap(sex_sim, plot=FALSE)
sex_obj$cols[1:length(sex_obj$cols)]<-colorRampPalette(colors=c("#4A4ACC", "orange"), space="Lab")(length(sex_obj$cols))
 plot(sex_obj)
```

```{r BI-palp, echo=FALSE, message=FALSE, warning=FALSE, verbose= FALSE, fig.width=6.5, fig.height=7, fig.cap= "Brownian Motion character map of palpon presence/absence on the consensus Bayesian tree topology." }
#Simmap PALPONS
palpons_obj <- densityMap(palpons_sim, plot=FALSE)
palpons_obj$cols[1:length(palpons_obj$cols)]<-colorRampPalette(colors=c("#4A4ACC", "orange"), space="Lab")(length(palpons_obj$cols))

plot(palpons_obj)
```

```{r tentilla-BI, echo=FALSE, message=F, warning=FALSE, verbose= FALSE, fig.width=6.5, fig.height=7, fig.cap= "Stochastic character map of presence of tentilla with *Physalia* included as not bearing tentilla, mapped on the consensus Bayesian tree topology."}
tentilla_obj <- densityMap(tentilla_sim,plot=FALSE)
tentilla_obj$cols[1:length(tentilla_obj$cols)]<-colorRampPalette(colors=c("#4A4ACC", "orange"), space="Lab")(length(tentilla_obj$cols))
plot(tentilla_obj)
```

```{r tentilla-ext-BI, echo=FALSE, message=F, warning=FALSE, verbose= FALSE, fig.width=6.5, fig.height=7, fig.cap= "Stochastic character map of presence of tentilla with *Physalia* included as bearing tentilla, mapped on the consensus Bayesian tree topology."}
tentilla2_obj <- densityMap(tentilla_sim2, plot=FALSE)
tentilla2_obj$cols[1:length(tentilla2_obj$cols)]<-colorRampPalette(colors=c("#4A4ACC", "orange"), space="Lab")(length(tentilla2_obj$cols))
plot(tentilla2_obj)
```

```{r nectosome-BI, echo=FALSE, message=F, warning=FALSE, verbose= FALSE, fig.width=6.5, fig.height=7, fig.cap= "Stochastic character map of presence of nectosome, mapped on the consensus Bayesian tree topology."}
nectosome_obj <- densityMap(nectosome_sim, plot=FALSE)
nectosome_obj$cols[1:length(nectosome_obj$cols)]<-colorRampPalette(colors=c("#4A4ACC", "orange"), space="Lab")(length(nectosome_obj$cols))
plot(nectosome_obj)
```

```{r mantle-BI, echo=FALSE, message=F, warning=FALSE, verbose= FALSE, fig.width=6.5, fig.height=7, fig.cap= "Stochastic character map of presence of a descending mantle canal in the nectophores, mapped on the consensus Bayesian tree topology."}
desc_mantle_obj <- densityMap(desc_mantle_sim, plot=FALSE)
desc_mantle_obj$cols[1:length(desc_mantle_obj$cols)]<-colorRampPalette(colors=c("#4A4ACC", "orange"), space="Lab")(length(desc_mantle_obj$cols))
plot(desc_mantle_obj)
```

```{r necto-BI, echo=FALSE, message=F, warning=FALSE, verbose= FALSE, fig.width=6.5, fig.height=7, fig.cap= "Stochastic character map for the evolution of the position of the nectosome, mapped on the consensus Bayesian tree topology."}
necto_pos_obj <- densityMap(necto_pos_sim, plot=FALSE)
necto_pos_obj$cols[1:length(necto_pos_obj$cols)]<-colorRampPalette(colors=c("#4A4ACC", "orange"), space="Lab")(length(necto_pos_obj$cols))
plot(necto_pos_obj)
```

```{r depth-BI, echo=FALSE, message=F, warning=FALSE, verbose= FALSE, fig.width=6.5, fig.height=7, fig.cap= "Brownian Motion character map of median depth of species observed with an MBARI ROV, mapped on the consensus Bayesian tree topology."}
depth_value = depth_median
depthmap <- contMap(dpruned_tree, depth_value, plot=F) %>% setMap(colors=c("cyan","blue","black"))
plot(depthmap)
```

```{r depth-BI-extended, echo=FALSE, message=F, warning=FALSE, verbose= FALSE, fig.width=6.5, fig.height=7, fig.cap= "Brownian Motion character map of median depth of species including blue water diving observations, mapped on the consensus Bayesian tree topology."}
median_extended = cdata$Depth.Median.Extended
names(median_extended) = rownames(cdata)
median_extended = median_extended[match(names(median_extended), ultratree$tip.label)]
depthmap_ext <- contMap(ultratree, median_extended, plot=F) %>% setMap(colors=c("cyan","blue","black"))
plot(depthmap_ext)

>>>>

All scripts for the analyses are available in a git repository at [https://github.com/caseywdunn/siphonophore_phylogeny_2017](https://github.com/caseywdunn/siphonophore_phylogeny_2017). The most recent commit at the time of the analysis presented here was `r system("git log | head -n 1", intern=TRUE) %>% str_replace("commit ", "") %>% strtrim(8)` with tag "paper_v2".

@@

RAxML ML analyses were conducted on the unpartitioned supermatrix using the WAG+$\Gamma$ model of amino acid substitution (Fig. \@ref(phylogeny)A). RAxML bootstrap values were estimated using `r length(bootstrap_trees)` replicates. IQTree ML analyses were run under JTT + Empirically counted frequencies from alignment + FreeRate model with 7 categories, the best model identified by ModelFinder, and the commonly used models GTR + Optimized base frequencies + Free rate model with 6 categories and WAG + Optimized base frequencies + Free rate model with 6 categories ((Fig. \@ref(fig:supplementary-trees))).

@@

Morphological character data used in trait mapping were obtained from the literature or direct observation of available voucher material. Depth distribution data was queried from the MBARI VARS database ( http://www.mbari.org/products/research-software/video-annotation-and-reference-system-vars/) [@schlining2006mbari]. We used stochastic character mapping to infer the most probable evolution of traits on the tree in R using the `phytools` package [@MEE3:MEE3169; @huelsenbeck2003stochastic]. For continuous character traits, model fit was tested using 
`fitContinuous` in the `geiger` R package. Subsequent analyses were conducted in R and integrated into this manuscript with the `knitr` package. See Supplementary Information for R package version numbers.

@@

Ancestral character state reconstructions favor the hypothesis that monoecy arose twice (Fig. \@ref(reconstruct)A and \@ref(fig:BI-mono)), once in Calycophorae and once in Clade A. This is consistent with differences in the arrangements of male and female gonophores in the two clades. In Clade A, male and female zooids are found within the same cormidium (a single reiterated sequence of zooids along the stem, see Fig. \@ref(colony)). In these species, the male and female zooids are placed at different but well defined locations within the cormidium. Meanwhile in calycophorans, each cormidium bears either male or female gonophores. In this form of monoecy, the male and female cormidia can either occur in an alternating pattern, or there can be several male or female cormidia in a row. In either case, male and female zooids are found at the same corresponding locations within the cormidia. One known exception to this can be found in abylid calycophorans, where both male or female gonophores may be found within the same eudoxid [@carre1967]. In sum, homoplasy in sexual-system evolution along with variation in the spatial arrangement of gonophores within a colony suggest that siphonophores have evolved different ways to be monoecious. The sexual system and cormidial arrangement of *Rudjakovia* is undescribed, although preliminary observations suggest that this species may be monoecious and that monoecy arose a third time in the Pyrostephidae. A detailed redescription of *Rudjakovia* would help clarify this.

@@

Within Calycophorae there are additional variations of the sexual mode: in *Sulculeolaria* (not included in this phylogeny) colonies appear to present a single sex at a time. However they are monoecious and protandrous, with female gonophores developing after the release of male gonophores [@carre1979]. Environmental influences may also play a role in determining the expressed sex. Colonies of the calycophoran *Chelophyes appendiculata* collected in the field always bear both male and female gonophores, whereas when kept in culture only gonophores of one sex are maintained [@Carre:2000hb]. This suggests a high plasticity of the sexual state in some calycophoran taxa and underlines the need for caution when evaluating the state of this character in rarely collected species.

@@

Palpons are typically defined as modified reduced gastrozooids [@mackie1987siphonophore]. In many species palpons are thought to play a role in digestion and circulation of the gastrovascular fluid, while other species may use them for defense (e.g *Physophora*) or sensory functions [@totton1965synopsis]. Palpons are subcategorised based on their location - palpons that are associated with gonodendra are termed gonopalpons (typically with a reduced tentacle, called a palpacle); palpons found along the stem of the siphosome are termed palpons (typically have a palpacle); and palpons found along the stem of the nectosome are termed nectosomal palpons (as in *Apolemia*) [@totton1965synopsis;@siebert2013re]. It is not clear how structure and function differs among different palpon subtypes, and a detailed histological investigation of palpons found at different locations within species is needed. For this reason, here we only assess the presence or absence of palpons as a category, without assessing subtypes of palpons. This presumes that palpons located at different regions in the colony are derived from other palpons rather than each arising *de novo* by independent modification of gastrozooids, a hypothesis that itself could be challenged upon closer histological examination of palpon diversity.

@@

This work was supported by the National Science Foundation (DEB-1256695, the Waterman Award, and DEB-1701272). CM was also supported in part by a RI-EPSCoR Fellowship, NSF EPS-1004057. Sequencing at the Brown Genomics Core facility was supported in part by NIH P30RR031153 and NSF EPSCoR EPS-1004057. Data transfer was supported by NSF RII-C2 EPS-1005789. Analyses were conducted with computational resources and services at the Center for Computation and Visualization at Brown University, supported in part by the NSF EPSCoR EPS-1004057 and the State of Rhode Island. SOWHAT analyses were carried out on the Odyssey cluster supported by the FAS Division of Science, Research Computing Group at Harvard University -- we thank Cassandra Extavour for use of the Harvard cluster. Analyses were also conducted on the Hoffman2 cluster of the Institute for Digital Research and Education of the University of California, Los Angeles. We thank Rob Sherlock for providing the *Bathyphysa conifera* photograph. We also thank Zack Lewis for help with RNA extractions and the MBARI crews and ROV pilots for collection of the specimens.
\clearpage

@@

@@

@@

@@

@@

@@

@@

@@

```{r BI-tree-trait-reconstructions, echo=FALSE, message=FALSE, warning=FALSE, verbose= FALSE, include=F}

@@

#Stochastic trait mapping:
#Make simmap objects
#print("SIMMAP Sex Distribution")
make.simmap(ultratree , sex, nsim = 100, message=FALSE) -> sex_sim_BI
#print("SIMMAP Palpons")
make.simmap(ultratree , palpons, nsim = 100, message=FALSE) -> palpons_sim_BI
#print("SIMMAP Tentilla")
make.simmap(ultratree , tentilla, nsim = 100, message=FALSE) -> tentilla_sim_BI
#print("SIMMAP Tentilla2")
make.simmap(ultratree , tentilla2, nsim = 100, message=FALSE) -> tentilla_sim2_BI
#print("SIMMAP Nectosome")
make.simmap(ultratree , nectosome, nsim = 100, message=FALSE) -> nectosome_sim_BI
#print("SIMMAP Nectosome Position")
make.simmap(ultratree , bracts, nsim = 100, message=FALSE) -> bracts_sim_BI
#print("SIMMAP Habitat")

#Nectophore position SIMMAP setup
NectoPosTree = drop.tip(ultratree , which(!(ultratree $tip.label %in% names(necto_pos))))
make.simmap(NectoPosTree, necto_pos, nsim = 100, message=FALSE) -> necto_pos_sim_BI

#Descending mantle Canal SIMMAP Setup
DescMantleTree =  drop.tip(ultratree , which(!(ultratree $tip.label %in% names(desc_mantle))))
make.simmap(DescMantleTree, desc_mantle, nsim = 100, message=FALSE) -> desc_mantle_sim_BI
```
\clearpage

![\label{bayesian}Bayesian (BI) CAT poisson phylogram with bipartition frequencies from the Bayesian posterior distribution of trees. Unlabeled nodes have support >0.99. The numbers of valid described species estimated to be in each clade based on taxonomy are shown below each clade name on the right.](supplementary_info/Supplementary_Figure11.pdf)

@@

```{r BI-mono, echo=FALSE, message=FALSE, warning=FALSE, verbose= FALSE, fig.width=6.5, fig.height=7, fig.cap= "Brownian Motion character map of sexual characters on the consensus Bayesian tree topology." }
#Simmap SEX
sex_obj_BI <- densityMap(sex_sim_BI, plot=FALSE)
sex_obj_BI$cols[1:length(sex_obj_BI$cols)]<-colorRampPalette(colors=c("#4A4ACC", "orange"), space="Lab")(length(sex_obj_BI$cols))
 plot(sex_obj_BI)
```

```{r BI-palp, echo=FALSE, message=FALSE, warning=FALSE, verbose= FALSE, fig.width=6.5, fig.height=7, fig.cap= "Brownian Motion character map of palpon presence/absence on the consensus Bayesian tree topology." }
#Simmap PALPONS
palpons_obj_BI <- densityMap(palpons_sim_BI, plot=FALSE)
palpons_obj_BI$cols[1:length(palpons_obj_BI$cols)]<-colorRampPalette(colors=c("#4A4ACC", "orange"), space="Lab")(length(palpons_obj_BI$cols))

plot(palpons_obj_BI)
```

```{r tentilla-BI, echo=FALSE, message=F, warning=FALSE, verbose= FALSE, fig.width=6.5, fig.height=7, fig.cap= "Stochastic character map of presence of tentilla with *Physalia* included as not bearing tentilla, mapped on the consensus Bayesian tree topology."}
tentilla_obj_BI <- densityMap(tentilla_sim_BI,plot=FALSE)
tentilla_obj_BI$cols[1:length(tentilla_obj_BI$cols)]<-colorRampPalette(colors=c("#4A4ACC", "orange"), space="Lab")(length(tentilla_obj_BI$cols))
plot(tentilla_obj_BI)
```

```{r tentilla-ext-BI, echo=FALSE, message=F, warning=FALSE, verbose= FALSE, fig.width=6.5, fig.height=7, fig.cap= "Stochastic character map of presence of tentilla with *Physalia* included as bearing tentilla, mapped on the consensus Bayesian tree topology."}
tentilla2_obj_BI <- densityMap(tentilla_sim2_BI, plot=FALSE)
tentilla2_obj_BI$cols[1:length(tentilla2_obj_BI$cols)]<-colorRampPalette(colors=c("#4A4ACC", "orange"), space="Lab")(length(tentilla2_obj_BI$cols))
plot(tentilla2_obj_BI)
```

```{r nectosome-BI, echo=FALSE, message=F, warning=FALSE, verbose= FALSE, fig.width=6.5, fig.height=7, fig.cap= "Stochastic character map of presence of nectosome, mapped on the consensus Bayesian tree topology."}
nectosome_obj_BI <- densityMap(nectosome_sim_BI, plot=FALSE)
nectosome_obj_BI$cols[1:length(nectosome_obj_BI$cols)]<-colorRampPalette(colors=c("#4A4ACC", "orange"), space="Lab")(length(nectosome_obj_BI$cols))
plot(nectosome_obj_BI)
```

```{r mantle-BI, echo=FALSE, message=F, warning=FALSE, verbose= FALSE, fig.width=6.5, fig.height=7, fig.cap= "Stochastic character map of presence of a descending mantle canal in the nectophores, mapped on the consensus Bayesian tree topology."}
desc_mantle_obj_BI <- densityMap(desc_mantle_sim_BI, plot=FALSE)
desc_mantle_obj_BI$cols[1:length(desc_mantle_obj_BI$cols)]<-colorRampPalette(colors=c("#4A4ACC", "orange"), space="Lab")(length(desc_mantle_obj_BI$cols))
plot(desc_mantle_obj_BI)
```

```{r necto-BI, echo=FALSE, message=F, warning=FALSE, verbose= FALSE, fig.width=6.5, fig.height=7, fig.cap= "Stochastic character map for the evolution of the position of the nectosome, mapped on the consensus Bayesian tree topology."}
necto_pos_obj_BI <- densityMap(necto_pos_sim_BI, plot=FALSE)
necto_pos_obj_BI$cols[1:length(necto_pos_obj_BI$cols)]<-colorRampPalette(colors=c("#4A4ACC", "orange"), space="Lab")(length(necto_pos_obj_BI$cols))
plot(necto_pos_obj_BI)
```

```{r depth-BI, echo=FALSE, message=F, warning=FALSE, verbose= FALSE, fig.width=6.5, fig.height=7, fig.cap= "Brownian Motion character map of median depth of species observed with an MBARI ROV, mapped on the consensus Bayesian tree topology."}
depth_value = depth_median
depthmap_BI <- contMap(dpruned_tree, depth_value, plot=F) %>% setMap(colors=c("cyan","blue","black"))
plot(depthmap_BI)
```

```{r depth-BI-extended, echo=FALSE, message=F, warning=FALSE, verbose= FALSE, fig.width=6.5, fig.height=7, fig.cap= "Brownian Motion character map of median depth of species including blue water diving observations, mapped on the consensus Bayesian tree topology."}
median_extended = cdata$Depth.Median.Extended
names(median_extended) = rownames(cdata)
median_extended = median_extended[match(names(median_extended), ultratree$tip.label)]
depthmap_ext_BI <- contMap(ultratree, median_extended, plot=F) %>% setMap(colors=c("cyan","blue","black"))
plot(depthmap_ext_BI)
```

\clearpage

```{r pdf-supplemental, verbose= FALSE, include=F, message = FALSE, echo=FALSE, comment=NA, warning=FALSE }
pdf("supplementary_info/Supplementary_Figure3.pdf")
plot(tentilla_obj)
dev.off()

pdf("supplementary_info/Supplementary_Figure4.pdf")
plot(tentilla2_obj)
dev.off()

pdf("supplementary_info/Supplementary_Figure5.pdf")
plot(nectosome_obj)
dev.off()

pdf("supplementary_info/Supplementary_Figure6.pdf")
plot(desc_mantle_obj)
dev.off()

pdf("supplementary_info/Supplementary_Figure7.pdf")
plot(necto_pos_obj)
dev.off()

pdf("supplementary_info/Supplementary_Figure8.pdf")
plot(depthmap)
dev.off()

pdf("supplementary_info/Supplementary_Figure10.pdf")
multiplot(p1, p2, p3, ncol=3)
dev.off()

pdf("supplementary_info/Supplementary_Figure12.pdf")
flip(p,calycophora_node,euphysonectae_node)
dev.off()

pdf("supplementary_info/Supplementary_Figure13.pdf")
plot(sex_obj_BI)
dev.off()

pdf("supplementary_info/Supplementary_Figure14.pdf")
plot(palpons_obj_BI)
dev.off()

pdf("supplementary_info/Supplementary_Figure15.pdf")
plot(tentilla_obj_BI)
dev.off()

pdf("supplementary_info/Supplementary_Figure16.pdf")
plot(tentilla2_obj_BI)
dev.off()

pdf("supplementary_info/Supplementary_Figure17.pdf")
plot(nectosome_obj_BI)
dev.off()

pdf("supplementary_info/Supplementary_Figure18.pdf")
plot(desc_mantle_obj_BI)
dev.off()

pdf("supplementary_info/Supplementary_Figure19.pdf")
plot(necto_pos_obj_BI)
dev.off()

pdf("supplementary_info/Supplementary_Figure20.pdf")
plot(depthmap_BI)
dev.off()

pdf("supplementary_info/Supplementary_Figure21.pdf")
plot(depthmap_ext_BI)
dev.off()
